\textsc{Atomic modeling of argon}\\ \footnotesize{\textsc{Project 5 --- FYS3150}}

### 2015-12-09 projects/project_5/molecular_dynamics/article/article.tex
added flowchart

\documentclass[a4paper]{article}
\usepackage[]{enumerate} 
\usepackage[]{graphicx} 
\usepackage[]{xcolor} 
\usepackage[]{subcaption} 
\usepackage[]{amsthm, amsmath, amssymb} 
\usepackage[]{fancyhdr}
\usepackage[]{setspace} 
\usepackage[]{hyperref} 
\urlstyle{sf}
\graphicspath{{../pictures/}}

@@

    \centering{\href{https://github.com/qTipTip/FYS3150}{\githublogo \,
    \color{gray!50}\textit{github.com/qTipTip}}}
\end{abstract}
\clearpage
\doublespacing
\tableofcontents
\listoffigures      
\singlespacing
\clearpage
\section{Introduction}
\label{sec:introduction}

@@

    The Maxwell-Boltzmann distribution is good for velocities because it fairly
    accurately represents the way velocities are distributed in an ideal gas.
    The distribution was defined initially by Maxwell, for the specific purpose
    of describing particle speeds inside a stationary container with no
    interaction.  The distribution is directly dependent on the temperature of
    the system as well as the mass of each particle. We want to initialize each
    atom with a random velocity given by the Maxwell-Boltzmann distribution.

    Mathematically, the distribution function reads
    \begin{equation}
        \notag
        P(v_i)\, dv_i = \left( \frac{m_i}{2\pi k_BT} \right)^{1/2} e^{-\frac{mv_i^2}{2k_BT}}dv_i
    \end{equation}

@@

\section{Simulations}
\label{sec:simulations}

@@

    \begin{figure}[h]
        \centering \includegraphics[width=\linewidth]{temperature_ratio.pdf}
        \caption[Temperature ratio]{Plotting the ratio between initial and
            instantaneous temperature for varying $T_i$. Each individual graph
            corresponds to one value of $T_i$ and the ratio is plotted against
            time given in units of tenths of a picosecond. Here the initial
            temperatures ranges from 20 to 500 kelvin, with 48 intermediate
            steps.  As we can see the ratio stabilizes around $1/2$. The graph of
            an arbitrary temperature has been highlighted in black.}
        \label{fig:temperature_ratio}
    \end{figure}

>>>>

\documentclass[a4paper]{article}
\usepackage[]{enumerate} 
\usepackage[]{graphicx} 
\usepackage[]{xcolor} 
\usepackage[]{subcaption} 
\usepackage[]{amsthm, amsmath, amssymb} 
\usepackage[]{fancyhdr}
\usepackage[]{setspace} 
\usepackage[]{tikz} 
\usetikzlibrary{shapes, arrows}
\usepackage[]{hyperref} 
\urlstyle{sf}
\graphicspath{{../pictures/}}

@@

    \centering{\href{https://github.com/qTipTip/FYS3150}{\githublogo \,
    \color{gray!50}\textit{github.com/qTipTip}}}
\end{abstract}
\clearpage
\doublespacing
\tableofcontents
\singlespacing
\listoffigures      
\clearpage
\section{Introduction}
\label{sec:introduction}

@@

    The Maxwell-Boltzmann distribution is good for velocities because it fairly
    accurately represents the way velocities are distributed in an ideal gas.
    The distribution was defined initially by Maxwell, for the specific purpose
    of describing particle speeds inside a stationary container with no
    interaction.  The distribution is directly dependent on the temperature of
    the system as well as the mass of each particle. We want to initialize each
    atom with a random velocity given by the Maxwell-Boltzmann distribution.
    Mathematically, the distribution function reads
    \begin{equation}
        \notag
        P(v_i)\, dv_i = \left( \frac{m_i}{2\pi k_BT} \right)^{1/2} e^{-\frac{mv_i^2}{2k_BT}}dv_i
    \end{equation}

@@

    \subsection{Program Flow}
    \label{sub:program_flow}

    A flow-chart describing the execution of the program can be seen in
    figure \ref{fig:flowchart}. I only a few of the more vital processes are
    described in detail.
    \begin{figure}[h]
        \centering \includegraphics[width=0.8\linewidth]{flow_chart.pdf}
        \caption[Flow chart]{A flow-chart of the program execution. The method
            \texttt{system.step} is described in more detail because it is what
            constitutes most of the program and is therefore included as a
        separate subprocess. The chart quite crude, and is meant to give an
    overarching idea of how the program executes.}
        \label{fig:flowchart}
    \end{figure}
\section{Simulations}
\label{sec:simulations}

@@

    \begin{figure}[h]
        \centering \includegraphics[width=0.8\linewidth]{temperature_ratio.pdf}
        \caption[Temperature ratio]{Plotting the ratio between initial and
            instantaneous temperature for varying $T_i$. Each individual graph
            corresponds to one value of $T_i$ and the ratio is plotted against
            time given in units of tenths of a picosecond. Here the initial
            temperatures ranges from 20 to 500 kelvin, with 48 intermediate
            steps.  As we can see the ratio stabilizes around $1/2$. The graph of
            an arbitrary temperature has been highlighted in black.}
        \label{fig:temperature_ratio}
    \end{figure}
